experiment 1

### 2021-08-12 experiments/experiment 1/experiment-1.Rmd
Analysis with least and most tolerant Sulfur Bacteria

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

```{r}
options(mc.cores = 12)
```

@@

@@

p2  <- plot_ss_result1(var_expt,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

>>>>

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
library(parallel)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

```{r}
options(mc.cores = detectCores())
```

@@

max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
#var_expt_levels[20,]
var_expt_copy <- var_expt
```

@@

```{r, fig.height=7.5, fig.width=12}

p2  <- plot_ss_result1_v2(var_expt,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

## Analysis with least and most tolerant Sulfur Bacteria

```{r}
##########################################
###### Setup copy-pasted from above

num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

num_div_treatment_levels <- 20

## rows of interest

var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)

## Overwriting average values with most and least tolerant values (tolerance and respective growth)

most_tolerant_PB <- var_expt[max_only_SBPB_diversity,]$pars[[1]]$PB
least_tolerant_PB <- most_tolerant_PB[which.min(most_tolerant_PB$h_O_PB),]
most_tolerant_PB <- most_tolerant_PB[which.max(most_tolerant_PB$h_O_PB),]

most_tolerant_SB <- var_expt[max_only_SBPB_diversity,]$pars[[1]]$SB
least_tolerant_SB <- most_tolerant_SB[which.min(most_tolerant_SB$h_O_SB),]
most_tolerant_SB <- most_tolerant_SB[which.max(most_tolerant_SB$h_O_SB),]

var_expt_most_tolerant_SBPB <- var_expt[no_diversity, ]
var_expt_most_tolerant_SBPB$pars[[1]]$PB[1:9] <- most_tolerant_PB
var_expt_most_tolerant_SBPB$pars[[1]]$SB[1:9] <- most_tolerant_SB
var_expt_most_tolerant_SBPB$pars[[1]]$PB$strain_name <- paste0("PB_",1:9)
var_expt_most_tolerant_SBPB$pars[[1]]$SB$strain_name <- paste0("SB_",1:9)

var_expt_least_tolerant_SBPB <- var_expt[no_diversity, ]
var_expt_least_tolerant_SBPB$pars[[1]]$PB[1:9] <- least_tolerant_PB
var_expt_least_tolerant_SBPB$pars[[1]]$SB[1:9] <- least_tolerant_SB
var_expt_least_tolerant_SBPB$pars[[1]]$PB$strain_name <- paste0("PB_",1:9)
var_expt_least_tolerant_SBPB$pars[[1]]$SB$strain_name <- paste0("SB_",1:9)
## number of cores usable
options(mc.cores = detectCores()-1)

## setup copy-pasted from above
default_sim_duration <- 1000000
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)
```

```{r eval=FALSE}
## Here the simulations with least and most tolerantsulfur bacteria are run.
var_expt <- var_expt_least_tolerant_SBPB
var_expt_least_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))

var_expt <- var_expt_most_tolerant_SBPB
var_expt_most_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
```

```{r, fig.height=7.5, fig.width=12}
var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))

plot_ss_result1_v2(var_expt_least_tolerant_SBPB,
                   result_index = 1,
                   filename_prefix = NULL,
                   save_image_file = FALSE) +
  plot_annotation(caption = 'Least tolerant SB and PB strains + average CB strain')

plot_ss_result1_v2(var_expt_most_tolerant_SBPB,
                   result_index = 1,
                   filename_prefix = NULL,
                   save_image_file = FALSE)+
  plot_annotation(caption = 'Most tolerant SB and PB strains + average CB strain')
```

```{r, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')
```
